Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum

### 2016-01-27 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd
Minor modifications

### Data preprocessing
```{r preprocess.data,cache=TRUE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER
```{r preprocess.data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

```{r get.gene.symbols, cache=TRUE}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl")

@@

>>>>

### Data preprocessing
```{r preprocess.data,cache=TRUE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER, based on the eucledian distance from other samples and/or seperated on the first 2 PC's
```{r preprocess.data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

```{r get.gene.symbols, cache=TRUE}
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "hsapiens_gene_ensembl", host = "www.ensembl.org")

@@

### Source Code
[This File](`r thisFile`)
